R Notebook for MSDepression Project

### 2021-02-08 dac_summary.Rmd
Add files via upload

data_e <- data4_20210119[which(data_empi_acc_f_phq$Provider %in% ms_providers),]
dep_df <- grep("F3", data_e$ICD10)
unique_empi <- match(unique(data_e$EMPI), data_e$EMPI)
num_unique_EMPI_and_dep <- sum(unique_empi %in% dep_df) #n = 469

@@

@@

eb_icd_and_phq2 <- data_e$ACCESSION_NUM[which(!is.na(data_e[dep_df,]$PHQ.2))] #n = 741
eb_icd_and_phq9 <- data_e$ACCESSION_NUM[which(!is.na(data_e[dep_df,]$PHQ.9))] #n = 106

@@

#unique empis
n_melissa_unique_empi <- length(unique(melissa_xls$EMPI[(unique(melissa_xls$ACCESSION_NUM) %in% unique(data_e$ACCESSION_NUM))]))

@@

print(paste0("n people in Melissa and EB overlap group, unique empi: ", n_melissa_unique_empi, " out of ", length(unique(data_e$ACCESSION_NUM))))

>>>>

data_e <- data4_20210119[which(data_empi_acc_f_phq$Provider %in% ms_providers),]
dep_df <- grep("F3", data_e$ICD10)
unique_empi <- which(unique(data_e$EMPI) %in% data_e$EMPI) #index of the locations of unique empis
num_unique_EMPI_and_dep <- sum(unique_empi %in% dep_df) #n = 469

@@

#summarize
print(paste0("N unique EMPIs in EB group = ", length(unique_empi), " out of ", dim(data_e)[1])) #

@@

eb_icd_and_phq2 <- data_e$ACCESSION_NUM[which(!is.na(data_e$PHQ.2[dep_df]))] #n = 741
eb_icd_and_phq9 <- data_e$ACCESSION_NUM[which(!is.na(data_e$PHQ.9[dep_df]))] #n = 106

@@

#unique empis
n_melissa_unique_empi <- sum(unique(melissa_xls$EMPI) %in% unique(data_e$EMPI))
n_melissa_unique_accession <- sum(unique(melissa_xls$ACCESSION_NUM) %in% unique(data_e$ACCESSION_NUM))

@@

print(paste0("n people in Melissa and EB overlap group, unique empi: ", n_melissa_unique_empi, " out of ", length(unique(data_e$EMPI))))

print(paste0("n people in Melissa and EB overlap group, unique accession #: ", n_melissa_unique_accession, " out of ", length(unique(data_e$ACCESSION_NUM))))

### 2021-02-08 lab_notebook.Rmd
Add files via upload

>>>>

#### 20210129

[x] figure out who has unique icd9/10 and phq2/9
[x] figure out what the overlap in # of scans between Melissa and my new group are

#### 20210208
[x] check logic of unique EMPIs, looks like something wonky is going on - less unique empis in my group than in the overlap group. Obviously they should be the same if not better
   - fixed, using accession #s and not empis to look for unique empis. Now that I look for unique EMPIs, we are all good!

#### 20210209
[] post to channel tomorrow
